### 2018-12-28 tim-lucas-wsc.tex
More edits.

Overall, model performance was good in Madagascar under both random and spatial cross-validation (Figure~\ref{f:scatter}).
Model performance was reasonable in Colombia under random cross-validation but poor under spatial cross-validation (Figure~\ref{f:scatter}).
This indicates that the covariates alone cannot explain malaria incidence in this area.
Mapped predictions of the best performing model look reasonable and are not unduly dominated by the random field.

@@

% models were quite good except spatial colombia
% which model performed best
% which ml model was best Vs parameters.
% parameters are negative and don't sum to one
%
% differences between models was less than difference between data.

@@

\begin{figure}
\centering
\includegraphics[trim={0 40mm 0 100mm}, width = 0.6\textwidth]{figs/col_obs_pred_map_ml.png} %\caption{Indonesia spatial crossvalidation} 
\caption{
  Left: Observed polygon data for Colombia. Grey indicates incidence of zero. Right: Out-of-sample predictions for the random cross-validation, machine learning model only model. For each cross-validation fold, predictions are made for the held out data. These predictions are all plotted which together covers the entire study area.
}
\label{randompredobspointfacet}
\end{figure}

>>>>

Overall, model performance was good in Madagascar under both random and spatial cross-validation (Figure~\ref{f:scatter}).
Model performance was reasonable in Colombia under random cross-validation but poor under spatial cross-validation (Figure~\ref{f:scatter}).
This indicates that the covariates alone cannot explain malaria incidence in this area.
Mapped predictions of the best performing model look reasonable and are not unduly dominated by the random field (Figure~\ref{f:map}).

@@

The cross-validation results for the machine learning models are shown in Table~\ref{t:ml results}.
Also in Table~\ref{t:ml results} is the means (across folds) of the  regression coefficients for these models from the polygon-level models that used only predictions from machine learning models as covariates.
Predictive performance was similar across different models, with Random Forest performing best in Madagascar and neural networks, Random Forests and elastic net performing equally well on Colombia.
The estimated regression parameters are similar between the random and spatial cross-validation schemes.
However, the best performing machibe learning models do not have the largest estimated regression coefficients.
Also of note is that some models were estimated to have a negative relationship (conditional on the presence of the other models) with polygon incidence.

% models were quite good except spatial colombia
% which model performed best
% Random field parameters?
% coverage
% which ml model was best Vs parameters.
% parameters are negative and don't sum to one
%
% differences between models was less than difference between data.

@@

\begin{figure}
\centering
\includegraphics[trim={0 40mm 0 100mm}, width = 0.6\textwidth]{figs/col_obs_pred_map_ml.png} %\caption{Indonesia spatial crossvalidation} 
\caption{
  Left: Observed polygon data for Colombia. Grey indicates incidence of zero. Right: Out-of-sample predictions for the random cross-validation, machine learning model only model. For each cross-validation fold, predictions are made for the held out data. These predictions are all plotted which together covers the entire study area.
}
\label{f:map}
\end{figure}
